Contention Management for 5G

### 2017-02-09 article/article.tex
pb

      \noindent {\bf Input:} a routage graph $\cal R$, an integer $\tau$ and an integer $P$.

      \noindent {\bf Question:} does there exist a $(P,\tau)$-periodic affectation of $\cal R$ ?

      We will prove in Sec.~\ref{sec:complexity} that the problem PRA is $\NP$-complete, even in restricted settings.
      Even approximating the smallest value of $P$ for which there is a $P$-periodic assignment is hard.
      Another strange property is that given a routage graph, we may have a $(P,\tau)$-periodic affectation but no
      $(P',\tau)$-periodic affectation with $P' > P$, the property is thus not monotone with regards to $P$.

	\begin{lemma} 
	 For any $P$, there is a routage graphe such that there is $(2,1)$-periodic affectation but no $(P,1)$-periodic affectation.
	\end{lemma}
\begin{proof}
      Consider the routage graph ${\cal R}$ given in the previous subsection. 
      We change the delays so that for $v$ the first vertex which belong to $r_i$ and $r_j$,
      we have $\lambda(v,r_i) - \lambda(v,r_j)= P$, where $P$ is an odd number smaller than $c$ the number of routes in ${\cal R}$.
      If we consider a period of $2$, for all $i \neq j$, $\lambda(v,r_i) - \lambda(v,r_j) = 1 $ modulo $2$. Therefore $(0,\dots,0)$ is a $(2,1)$-periodic affectation of ${\cal R}$.
      On the other hand, if we want to find a $(P,1)$-periodic affectation, then $\lambda(v,r_i) - \lambda(v,r_j) = 0 $ modulo $P$.
      Thus we must find $m_i \in \{0,\dots,P-1\}$ such that for all $i \neq j \in \{1,\dots,c\}^2$, $m_i \neq m_j$, which is impossible since $P < c$.

@@

      In the context of cloud-RAN applications, we consider here the digraph $G=(V,A)$ modeling the target network 
      and two disjoint subsets of vertices $S$ and $L$, where $S$ is the set of BBU and $L$ is the set of RRH. 
      We denote by $n$ the size of $S$ and $L$. We are given a period $P$, a routing function ${\cal R}$ and a bijection $\rho:L\rightarrow S$ which assigns a BBU to each RRH. Let ${\cal C}_{\rho} = \{(l,\rho(l))\}_{l \in L} \cup \{(s,\rho^{-1}(s))\}_{s \in S}$. Let consider a $P$-periodic affectation of ${\cal C}_{\rho}$ which associates $m_l$ to 
      $(l,\rho(l))$ and $m_{\rho(l)}$ to $(\rho(l),l)$.

      This affectation represents the following process: first a message is sent in $l$, through the route $r_l$, at time $m_l$.
      This message is received by $\rho(l)$ at time $t(\rho(l),r_l)$. It is then sent back to $l$ in the same period at time $m_{\rho(l)}$ if $m_{\rho(l)} > t(\rho(l),r_l)$, otherwise at time $m_{\rho(l)}$ in the next period. The time between the arrival of the message and the time it is sent back is called the \textbf{waiting time} and is defined by $w_l = m_{\rho(l)} - t(\rho(l),r_l)$ if $m_{\rho(l)} > t(\rho(l),r_l)$ and $w_l = m_{\rho(l)} + P - t(\rho(l),r_l)$ otherwise.
      When a BBU receives a message, it must compute the answer before sending it back to the RRH. This time can be encoded
      in the last arc leading to the BBU and thus we need not to consider it explicitely in our model.

      Thus, the whole proccess time for a vertex $l$ is equal to
      $$
      PT(l)=\lambda(r_l)+ w_l+\lambda(r_{\rho(l)}).
      $$

    The {\bf maximum process time} of the $P$-periodic affectation ${\cal M} $ is defined by $MT({\cal M})=\max\limits_{l \in L} PT(l)$. The problem we want to solve is the following.

@@

      \noindent {\bf Input:}  a digraph $G$, a matching $\rho$ from $L$ to $S$ two disjoint set of vertices of $G$, a routing function $\cal R$, a period $P$, an integer $T_{max}$.

@@

    \node (2) at (-7,-2){\Huge G};
    \node (3) at (10,-2){\Huge H};
    \end{tikzpicture}

>>>>

      \noindent {\bf Input:} a routage graph $\cal R_{\cal C}$, an integer $\tau$ and an integer $P$.

      \noindent {\bf Question:} does there exist a $(P,\tau)$-periodic affectation of $\cal R_{\cal C}$ ?

      We will prove in Sec.~\ref{sec:complexity} that the problem PRA is $\NP$-complete, even in restricted settings.
      Even approximating the smallest value of $P$ for which there is a $(P,\tau)$-periodic affectation is hard.
      Another strange property is that given a routage graph, we may have a $(P,\tau)$-periodic affectation but no
      $(P',\tau)$-periodic affectation with $P' > P$, the property is thus not monotone with regards to $P$.

	\begin{lemma} 
	 For any $P$, there is a routage graphe such that there is $(2,1)$-periodic affectation but no $(P,1)$-periodic affectation.
	\end{lemma}
\begin{proof}
      Consider the routage graph ${\cal R_{\cal C}}$ given in the previous subsection. 
      We change the delays so that for $v$ the first vertex which belong to $r_i$ and $r_j$,
      we have $\lambda(v,r_i) - \lambda(v,r_j)= P$, where $P$ is an odd number smaller than $c$ the number of routes in ${\cal R}$.
      If we consider a period of $2$, for all $i \neq j$, $\lambda(v,r_i) - \lambda(v,r_j) = 1 $ modulo $2$. Therefore $(0,\dots,0)$ is a $(2,1)$-periodic affectation of ${\cal R}$.
      On the other hand, if we want to find a $(P,1)$-periodic affectation, then $\lambda(v,r_i) - \lambda(v,r_j) = 0 $ modulo $P$.
      Thus we must find $m_i \in \{0,\dots,P-1\}$ such that for all $i \neq j \in \{1,\dots,c\}^2$, $m_i \neq m_j$, which is impossible since $P < c$.

@@

      In the context of cloud-RAN applications, we consider here the digraph $G=(V,A)$ modeling the target network 
      and two disjoint subsets of vertices $S$ and $L$, where $S$ is the set of BBU and $L$ is the set of RRH. 
       We have as much BBUs as RRH in the network. We denote by ${\cal c}$ the size of $S$ and $L$, and so, the number of routes.
       We are given a period $P$, a routing function ${\cal R}$, and an assignment ${\cal C}:L\rightarrow S$  which assigns a BBU to each RRH. 
       $l_i,i<{\cal c}$ is the RRH of the route $i$ and ${\cal C}(l_i)$, or $s_i$ is its corresponding BBU. The routing between each RRH and BBU is given by the routage graph ${\cal R}_{\cal C}$.

       Let consider a $(P,\tau)$-periodic affectation of ${\cal R}_{\cal C}$ which associates $m_l$ to 
      $(l,{\cal C}(l))$ and $m_{{\cal C}(l)}$ to $({\cal C}(l),l)$.

%       
%       We denote by $n$ the size of $S$ and $L$. We are given a period $P$, a routing function ${\cal R}$ and a bijection $\rho:L\rightarrow S$ which assigns a BBU to each RRH. Let ${\cal C}_{\rho} = \{(l,\rho(l))\}_{l \in L} \cup \{(s,\rho^{-1}(s))\}_{s \in S}$. Let consider a $P$-periodic affectation of ${\cal C}_{\rho}$ which associates $m_l$ to 
%       $(l,\rho(l))$ and $m_{\rho(l)}$ to $(\rho(l),l)$.

      This affectation represents the following process: first a message is sent in $l$, through the route $r_l$, at time $m_l$.

      \begin{center}
      \includegraphics[scale=0.2]{rrh.jpeg}
      \end{center}

      This message is received by ${\cal C}(l)$ at time $t({\cal C}(l),r_l)$. It is then sent back to $l$ in the same period at time $m_{{\cal C}(l)}$ if $m_{{\cal C}(l)} > t({\cal C}(l),r_l)$, otherwise at time $m_{{\cal C}(l)}$ in the next period. The time between the arrival of the message and the time it is sent back is called the \textbf{waiting time} and is defined by $w_l = m_{{\cal C}(l)} - t({\cal C}(l),r_l)$ if $m_{{\cal C}(l)} > t({\cal C}(l),r_l)$ and $w_l = m_{{\cal C}(l)} + P - t({\cal C}(l),r_l)$ otherwise.

       \begin{center}
      \includegraphics[scale=0.2]{BBU1.jpeg}

      \includegraphics[scale=0.2]{BBU2.jpeg}
      \end{center}

      When a BBU receives a message, it must compute the answer before sending it back to the RRH. This time can be encoded
      in the last arc leading to the BBU and thus we need not to consider it explicitely in our model.

      Thus, the whole proccess time for a vertex $l$ is equal to
      $$
      PT(l)=\lambda(r_l)+ w_l+\lambda(r_{{\cal C}(l)}).
      $$

    The {\bf maximum process time} of the $(P,\tau)$-periodic affectation ${\cal M} $ is defined by $MT({\cal M})=\max\limits_{l \in L} PT(l)$. The problem we want to solve is the following.

@@

      \noindent {\bf Input:}  A routage graph ${\cal R}_{\cal C}$, a period $P$, an integer $T_{max}$.

@@

    \node (2) at (-7,0){\Huge H};
    \node (3) at (10,0){\Huge G};
    \end{tikzpicture}
